|

### 2022-06-23 docs/rmd/paper.tex
autogit

All GP experiments will be implemented by using the python programming
language in conjunction with DEAP, a framework for distributed
evolutionary algorithms that implements various tools and algorithms for
genetic programming (Fortin \emph{et al.}, 2012). A github repository
that contains the full source code, tables, plots and other materials
represented in this thesis can be accessed at
\protect\hyperlink{https:ux2fux2fgithub.comux2froman91DEux2fintelligent_information_systems_research_project}{https://github.com/roman91DE/intelligent\_information\_systems\_research\_project}

>>>>

All GP experiments will be implemented by using the python programming
language in conjunction with DEAP, a framework for distributed
evolutionary algorithms that implements various tools and algorithms for
genetic programming (Fortin \emph{et al.}, 2012). A github repository
that contains the full source code, tables, plots and other materials
represented in this thesis can be accessed at
\protect\hyperlink{https:ux2fux2fgithub.comux2froman91DEux2fintelligent_information_systems_research_project}{https://github.com/roman91DE/intelligent\_information\_systems\_research\_project}.
